---
title: "BRIEF Data Processing"
author: "Alison Luongo"
date: "9/21/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(naniar)
library(readxl)
```

```{r, results='hide', include=FALSE}
data <- read_xlsx("BRIEF_Project_9-23-21.xlsx")


data <- data %>% replace_with_na_all(condition =~.x == -999)
```


| Number | Child's Ethnicity              | Maternal Education                    | Household Income | 
|:------:|:------------------------------:|:-------------------------------------:|:----------------:|
|1       |White, Non-Hispanic             |0-11 Years                             |< $10,000         |
|2       |Black, Non-Hispanic             |Graduated High School/GED              |$10,000-$25,000   |
|3       |White, Hispanic                 |Some College or Technical School       |$25,000-$50,000   |
|4       |Black, Hispanic                 |Graduated Associated/Technical School  |$50,000-$75,000   |
|5       |American Indian/Alaskan Native  |Graduated with Bachelor's Degree       |$75,000-$100,000  |
|6       |Asian/Pacific Islander          |Some Graduate School                   |> $100,000        |
|7       |Biracial/Multicultural/Other    |Completed Graduate (MS,PHD,MD,JD)      |N/A           

Household Income Recode: 1 = under $50K, 2 = over $50K

**0 = No | 1 = Yes | -999 = Missing/Unanswered | Blank = N/A**

Age Determined as the date of the first day of actigraphy - birthday

1 - Infant: 0-0:11 
2 - Toddler: 1-2:11 
3 - Preschool: 3-4:11
4 - Child/School: 5-11:11
5 - Teenager: 12-17:11
6 - Young Adult: 18-25+

# BRIEF Project Inclusion Information

+ 2-17.99 Years Old
+ Only DS Participants
+ Complete BRIEF

NOTE: These BRIEF might have been completed, but their data might not have been entered completely (which is probably the case for a lot of participants in this dataset). Many participants also did not indicate when the BRIEF was completed, so it's not possible to calculate their age. These participants will be excluded for now. 

Get rid of TD participants
```{r}
library(dplyr)
DS_Data <- data %>% filter(Group=="DS")
```

Biological Information Included: Hearing Problems, Vision Problems, ASD Dx, Prematurity (we don't have), Sleep Disorder, heart Defect (congenital in our data), DS type (don't have entered), ADHD, OCD (we don't have), Tourette's (we don't have), Leukemia (we don't have), Thyroid (endocrine in our dataset), GI concerns (we don't have), Diabetes (some have, not all), Seizures (some have data on this but not all), head injury

Other info included: sex, demographics, MB-CDI, VABS (we don't have), SIB-R, KBIT, Leiter (we don't have), Baley (we don't have)

We also have PPVT, but it doesn't look like they're interested in that data. Since they want language outcomes, I'll include these anyways.
```{r}
DS_Data <- subset(DS_Data, select=c(Karyotype, Group, Study, Gender, Gender_Num, Participant_Number, DOB, BRIEF_Date, Age_BRIEF, Age_Actigraphy, Child_Ethnicity, Maternal_Ethnicity, Maternal_Education, Maternal_Education_Years, Household_Income, Household_Income_Recode, Autism_Diagnosis, ADHD_Diagnosis, adhd, Sleep_Apnea_Diagnosis, visual_impairment, hearing_loss, Congenital_disorders, head_injury_trauma, head_injury_loc, heart_defect, leukemia_blood_disease, seizure_convulsion, hypothyroidism, diabetes, endocrine_issues, KBIT_Date, KBIT_Age, Verbal_Knowledge_Raw:IQ_Composite_SS, briefpre_inhibit_tscore, briefpre_shift_tscore, briefpre_ec_tscore, briefpre_working_mem_tscore, briefpre_po_tscore, briefpre_isci_tscore, briefpre_fi_tscore, briefpre_emi_tscore, briefpre_gec_tscore, inhibit_tscore, self_monitor_tscore, bri_tscore, shift_tscore, ec_tscore, eri_tscore, initiate_tscore, working_mem_tscore, po_tscore, tm_tscore, org_of_mat_tscore, cri_tscore, gec_tscore, AE:SIBR_Sum_All, Support_Score, CDIAge_WS:UnderstoodWords_WG, ppvt4_test_date:NisongerOverlySensitive))
```

Note: BRIEF PReschool is labeled, briefpre_, the BRIEF Parent is not labeled, if just has the category and t-score --- easy to change later if necessary.

SIB-R: AW-SMI, Support Score

Age_At_Brief is a calculation, so when its loaded into the data it's loaded as a character which we don't want. I copied these values and pasted them into Age_Brief, so they should be coded as numeric. Let's check:
```{r}
str(DS_Data$Age_BRIEF)
```


Only include participants 2-17.99 years old
```{r}
DS_BRIEF <- DS_Data %>% filter(Age_BRIEF > 1.99)
DS_BRIEF <- DS_Data %>% filter(Age_BRIEF < 17.99)
```

144 with DS in this age range who indicated when their BRIEF was completed. 

Number of participants with multiple entries in the dataset:
```{r}
n_distinct(DS_BRIEF$Participant_Number[duplicated(DS_BRIEF$Participant_Number)])
```
5

Separate into Brief Parent and Brief Preschool
```{r}
DS_BRIEF_Pre <- DS_BRIEF %>% filter(!is.na(briefpre_inhibit_tscore))
DS_BRIEF_Pre <- subset(DS_BRIEF_Pre, select = -c(inhibit_tscore:gec_tscore))

DS_BRIEF_Par <- DS_BRIEF %>% filter(!is.na(inhibit_tscore))
DS_BRIEF_Par <- subset(DS_BRIEF_Par, select = -c(briefpre_inhibit_tscore:briefpre_gec_tscore))
```

```{r}
n_distinct(DS_BRIEF_Pre$Participant_Number[duplicated(DS_BRIEF_Pre$Participant_Number)])
n_distinct(DS_BRIEF_Par$Participant_Number[duplicated(DS_BRIEF_Par$Participant_Number)])
```
Preschool: No repeated participants
Parent: 5 repeated participants

```{r}
n_distinct(DS_BRIEF_Pre$Participant_Number)
n_distinct(DS_BRIEF_Par$Participant_Number)
```
Brief Preschool: 49
Brief Parent: 88

Age Ranges:
```{r}
range(DS_BRIEF_Pre$Age_BRIEF)
```
2-2.18

```{r}
range(DS_BRIEF_Par$Age_BRIEF)
```
6.52-17.33

Summary of the Data (Range, max, mins, NAs, etc.)
PRESCHOOL:
```{r}
summary(DS_BRIEF_Pre)
```

PARENT:
```{r}
summary(DS_BRIEF_Par)
```





